Low Dimensional Embedding of Climate Data for Radio Astronomical Site Testing in the Colombian Andes

### 2017-05-09 pasp/paperclimate.tex
penultimos cambios de oleonardo

There is an additional issue with the Valle del Sol region. The high industrial activity in this region could fill the air with particulate material, which would nullify the suitability of this region. Besides obtaining seasonal high-resolution precipitable water vapor maps, in our next paper we will study the amount of particulate material in this region using MODIS (Aqua and Terra) satellite data.\\

The methods used here can be extended and adapted to similar climatological datasets for other countries. This can be a first step in radio astronomy site testing for developing nations.

>>>>

There is an additional issue with the Valle del Sol region. The high industrial activity in this region fills the air with particulate material \cite{sogphd,sogamoso}, which would nullify the suitability of this region. Besides obtaining seasonal high-resolution precipitable water vapor maps, in our next paper we will study the amount of particulate material in the reported regions of interest using MODIS (Aqua and Terra) satellite data.\\

The methods used here can be extended and adapted to similar climatological datasets in other regions. This can be a preliminary step in radio astronomy site testing in developing countries.
